RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-02-03 assets/illustration/ambc.tex
:lipstick: Update illustrations and reference

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.25,1) -- (0.75,3);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[magenta,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (5.11,3.5) -- (2.5,3.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (7.43,3.28) -- (8,1);
	\draw[lightgray,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (7.525,2.9) -- (8,1);

>>>>

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.25,1) -- (0.75,3);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[magenta,decorate,decoration={crosses,segment length=16mm,shape size=1.5mm}] (5.11,3.5) -- (2.5,3.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (7.43,3.28) -- (8,1);
	\draw[lightgray,decorate,decoration={crosses,segment length=16mm,shape size=1.5mm}] (7.525,2.9) -- (8,1);
